---
title: "coefficient significance comparison for different measures of income"
author: "DLu"
date: "October 27, 2015"
output: pdf_document
---
Initialize doc:
```{r, echo = FALSE}
WD <- "D:/GoogleDrive/Work/MSc_Thesis/2_data"
setwd(WD)
require(plm)
require(xts)
require(reshape2)
load("knitworkspace.RData")
```

Prints the output of coefficient significance for two estimations, one using
nominal income measures, one using real income measures (not normalized to the
starting year)


\pagebreak
\textbf{FOR DFE MODEL (dynamic fixed effect)}

```{r, echo=TRUE }
my.coef.nominal$coeff.legend
summary(my.coef.nominal$details$dfe.result)
summary(my.coef.real$details$dfe.result)
```

\textbf{Significant Coefficients}
\begin{tabular}{p{2cm}|p{5cm}|p{5cm}}
category &
  nominal &
  real\\ \hline
LR coef &
  y, x1, x2 &
  y, x1\\
SR coef & 
  y all lags, x1 all lags, x2 0-lag, x3 3-4 lag, x4 1-4 lag (0 amplitude)&
  y all lags, x1 1-4 lag,   , x3 3-4 lag, x4 3-4 lag (0 amplitude)\\
\end{tabular}

\textbf{dfe.result interpretation}

LR:

 - x1 (nominal income): 10% increase in x1 (pop) causes 4.7% increase in y (price)
 - x1 (real income): 10% increase in x1 (pop) causes 3.9% increase in y (price)

SR for nominal income

 - x3 (hstock) 3-lag: +1% x3 = +38.5% in y (price)
 - x3 (hstock) 4-lag: +1% x3 = -20% in y(price) 

SR for real income:

 - x3 (hstock) 3-lag: +1% x3 = +42% in y
 - x3 (hstock) 4-lag: +1% x3 = -20% in y


BUT GM DOES NOT SHOW ANY SIGNIFICANT COEFFICIENTS IN THE LONG RUN FOR ANY OF THE
FACTORS (except lagged price)

\pagebreak
\textbf{FOR GROUP MEAN ESTIMATOR (GM)}

```{r, echo=TRUE }
my.coef.nominal$coeff.legend
summary(my.coef.nominal$details$gm.pmg)
summary(my.coef.real$details$gm.pmg)
```

